Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-17 paper/paperv3.qmd
Adding the random effect of year back into the detection probability plot

# Yearly predictions
detection_pred_years <- detection_grid %>% 
  mutate(predicted = predict(detection_mod, 
                             newdata = .,
                             type = "response",
                             re.form = ~ (1 | year_fct)))

ggplot(detection_pred, aes(age)) +
  # Line per year
  geom_line(aes(y = predicted, group = interaction(age, year_fct)), 
            detection_pred_years, 
            alpha = 0.2) +
  # Weighted model
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              alpha = 0.3, 
              color = NA) +
  geom_line(aes(y = predicted),
            linewidth = 1.5) +
  # Population-level model
  geom_line(aes(y = pred_pop), 
            linetype = "dotted",
            linewidth = 1.1) +
  # Raw data
  geom_pointrange(aes(y = observed_mean, 
                      ymin = observed_lwr, 
                      ymax = observed_upr),
                  detection_summ) +
  # Sample size
  geom_text(aes(age, label = n), detection_summ, y = 0, vjust = 0) +
  scale_x_continuous("Age", breaks = seq(4, 19, by = 4)) +
  scale_y_continuous("Detection rate", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA)) +
  # scale_linetype_manual(values = c("solid", "dashed")) +
  # scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  # scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  theme(legend.position = "none")
```

>>>>

# Yearly predictions
detection_pred_years <- detection_grid %>% 
  mutate(predicted = predict(detection_mod, 
                             newdata = .,
                             type = "response",
                             re.form = ~ (1 | year_fct))) %>% 
  group_by(age, year_fct)

  geom_line(aes(age, predicted, group = interaction(phase, age_cat, year_fct)), 
            filter(phen_pred_years, phase == "breeddur"),
            alpha = 0.1) +

ggplot(detection_pred, aes(age)) +
  # Line per year
  geom_line(aes(x = age, y = predicted, group = interaction(age_cat, year_fct)), 
            mutate(detection_pred_years, age_cat = "all"), 
            alpha = 0.2) +
  # Weighted model
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high),
              alpha = 0.3, 
              color = NA) +
  geom_line(aes(y = predicted),
            linewidth = 1.5) +
  # Population-level model
  geom_line(aes(y = pred_pop), 
            linetype = "dotted",
            linewidth = 1.1) +
  # Raw data
  geom_pointrange(aes(y = observed_mean, 
                      ymin = observed_lwr, 
                      ymax = observed_upr),
                  detection_summ) +
  # Sample size
  geom_text(aes(age, label = n), detection_summ, y = 0, vjust = 0) +
  scale_x_continuous("Age", breaks = seq(4, 19, by = 4)) +
  scale_y_continuous("Detection rate", 
                     labels = scales::label_percent(accuracy = 1),
                     limits = c(0, NA)) +
  theme(legend.position = "none")
```
